\documentclass[a4paper]{article}
\usepackage[english]{babel}
\usepackage{fullpage}
\usepackage{emp}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{listings}
\graphicspath{{./UML/}}
\usetikzlibrary{shapes,snakes}
\usepackage{multirow}
\usepackage{color}
\usepackage{float}
\usepackage{subfigure}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\title{Software Ontwerp - Verslag Iteratie 2\\Prof. T. Holvoet\\Dhr. T. Heyman}
\author{Team 08:\\Willem Van Onsem\\Jonas Vanthornhout\\Pieter-Jan Vuylsteke}
\date{24 december 2010}

\begin{document}
\begin{empfile}
\begin{titlepage}
\begin{center}
\HRule \\[0.4cm]
{ \huge \bfseries Domain Model and Refactoring Report}\\[0.4cm]
\HRule \\[1.5cm]
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Professor:}\\
T. \textsc{Holvoet}\\
\emph{Begeleider:}\\
T. \textsc{Heyman}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Team 08:} \\
Willem \textsc{Van Onsem}\\
Jonas \textsc{Vanthornhout}\\
Pieter-Jan \textsc{Vuylsteke}
\end{flushright}
\end{minipage}

\vfill

% Bottom of the page
{\large \today}
%\maketitle
\end{center}
\end{titlepage}
\newpage
\section{Domain model}
\section{Terminology}

\begin{description}
  \item[FireTruck:] A fire truck is a normal unit, except that there is a maximum size of fire it is capable of dealing with. The capacitiy of a fire truck is expressed in liters of water.
  \item[Disaster:] A disaster consists of multiple emergencies regarding the same event.
  \item[Ambulance:] An ambulance responds to emergencies with victims. When an ambulance arrives at the location of an emergency, it picks up a victim and transports him/her to a hospital. An ambulance can carry two victims at once if needed, but can also transport a single victim. An ambulance has finished its task if the victim is delivered at the hospital. 
  \item[Dispatcher:] A person working at the dispatch center, handling emergencies or disasters by assigning units to respond to the emergency or disaster. Dispatchers are identified by their name. \textbf{(Moet er nog iets over gezegd worden dat hij disasters kan cre\"eren? Maar dat klinkt dan ook weer zo raar.)}
  \item[Unit:] A unit can be an Ambulance, PoliceCar or FireTruck, which are identified by a name, have a home location (its station) and a current location. Units can be assigned to an emergency or disaster by a dispatcher, which means they will respond to the emergency or disaster by going to its location and executing their task (e.g. putting out a fire). A unit can only be assigned to one emergency or disaster at once. The unit commander notifies the system when a unit has finished its current assignment, after which it can be reassigned to another emergency or disaster. When a unit is not assigned to an emergency or disaster, it returns to its home location.
\end{description}
\section{Refactorings}
\end{empfile}
\end{document}
